The Astropy Project:

### 2017-09-29 main.tex
accuracy subsection
new features

Accuracy and comparison of coordinate system definitions?

\textbf{Key new features:}
\begin{itemize}
	\item Celestial coordinates, and local coordinates (via EarthLocation + Time)
    \item differential classes
    \item Proper motions, radial velocities
    \item JPL ephemerids
\end{itemize}

Separately, talk about representations as vectors? (MHvK)

>>>>

\textbf{Key new features:}
\begin{itemize}
	\item Celestial coordinates, but now also local coordinates (via EarthLocation + Time)
    \item differential classes
    \item Proper motions, radial velocities
    \item JPL ephemerids
\end{itemize}

\subsubsection{Accuracy and comparison of coordinate system definitions?}
% Erik?
